Larkin Secondary CREP

### 2024-02-12 analysis/analyses.Rmd
fixing links to data
updating julie analysis

```{r}
load("full_long.Rdata")
```

@@

```{r}
ggplot(DF, aes(j_cond, j_know_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Knowledge Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))
```

@@

```{r}
ggplot(DF, aes(j_cond, j_reason_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Reasonable Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))
```

@@

```{r}
ggplot(DF, aes(j_cond, j_luck_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Luck Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))
```
## Forced Choice

@@

tknow %>% 
  ggplot(aes(fill = knowledge_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Knowledge Attribution by Condition and Expertise", fill="knowledge_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Knowledge Attribution", start = .9, end=0, labels = c("Believes", "Knows")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  
```

@@

treason %>% 
  ggplot(aes(fill = reasonable_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Reasonable Attribution by Condition and Expertise", fill="reasonable_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Reasonable Attribution", start = .9, end=0, labels = c("Reasonable", "Unreasonable")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  
```

@@

tluck %>% 
  ggplot(aes(fill = luck_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Ability/Luck Attribution by Condition and Expertise", fill="luck_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Ability/Luck Attribution", start = .9, end=0, labels = c("Ability", "Luck")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  
```

@@

tknow %>% 
  ggplot(aes(fill = knowledge_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Knowledge Attribution by Condition and Expertise", fill="knowledge_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Knowledge Attribution", start = .9, end=0, labels = c("Believes", "Knows")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  
```

@@

treason %>% 
  ggplot(aes(fill = reasonable_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Reasonable Attribution by Condition and Expertise", fill="reasonable_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Reasonable Attribution", start = .9, end=0, labels = c("Reasonable", "Unreasonable")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  
```

@@

tluck %>% 
  ggplot(aes(fill = luck_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Inability/Luck Attribution by Condition and Expertise", fill="luck_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Ability/Luck Attribution", start = .9, end=0, labels = c("Ability", "Luck")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)  
```

>>>>

```{r}
load("../data/full_long.Rdata")
```

@@

```{r}
ggplot(DF, aes(j_cond, j_know_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Knowledge Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))

ggsave("figures/fig_1.png", dpi = 300)
```

@@

```{r}
ggplot(DF, aes(j_cond, j_reason_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Reasonable Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))

ggsave("figures/fig_2.png", dpi = 300)
```

@@

```{r}
ggplot(DF, aes(j_cond, j_luck_vas, color = j_expertise, fill = j_expertise)) + 
  stat_summary(fun = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2, 
               color = "black") +
  xlab("Vignette Condition") + 
  ylab("Luck Visual Analog Scale") + 
  theme_classic() + 
  scale_fill_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey")) + 
  scale_color_manual(name = "Expertise", labels = c("Naive", "Expert"), values = c("darkgrey", "lightgrey"))

ggsave("figures/fig_3.png", dpi = 300)
```
## Forced Choice

@@

tknow %>% 
  ggplot(aes(fill = knowledge_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Knowledge Attribution by Condition and Expertise", fill="knowledge_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Knowledge Attribution", start = .9, end=0, labels = c("Believes", "Knows")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)

ggsave("figures/fig_4.png", dpi = 300)
```

@@

treason %>% 
  ggplot(aes(fill = reasonable_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Reasonable Attribution by Condition and Expertise", fill="reasonable_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Reasonable Attribution", start = .9, end=0, labels = c("Reasonable", "Unreasonable")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)

ggsave("figures/fig_5.png", dpi = 300)
```

@@

tluck %>% 
  ggplot(aes(fill = luck_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Ability/Luck Attribution by Condition and Expertise", fill="luck_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Ability/Luck Attribution", start = .9, end=0, labels = c("Ability", "Luck")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)

ggsave("figures/fig_6.png", dpi = 300)
```

@@

tknow %>% 
  ggplot(aes(fill = knowledge_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Knowledge Attribution by Condition and Expertise", fill="knowledge_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Knowledge Attribution", start = .9, end=0, labels = c("Believes", "Knows")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)

ggsave("figures/fig_7.png", dpi = 300)
```

@@

treason %>% 
  ggplot(aes(fill = reasonable_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Reasonable Attribution by Condition and Expertise", fill="reasonable_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Reasonable Attribution", start = .9, end=0, labels = c("Reasonable", "Unreasonable")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)

ggsave("figures/fig_8.png", dpi = 300)
```

@@

tluck %>% 
  ggplot(aes(fill = luck_attribution, y = Frequency, x = Expertise)) +
  labs("Figure X. Rates of Inability/Luck Attribution by Condition and Expertise", fill="luck_attribution") +
  geom_bar(position="fill", stat = "identity") +
  scale_y_continuous(labels=scales::percent) +
  ylab("Percentage Respondents") +
  scale_fill_grey(name = "Ability/Luck Attribution", start = .9, end=0, labels = c("Ability", "Luck")) +
  theme_bw()+theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1)) + 
  facet_wrap(~j_condition)

ggsave("figures/fig_9.png", dpi = 300)
```
